Finding points on varieties with \emph{Macaulay2}

### 2023-05-17 FastLinAlg/Paper/RandomRationalPoints.tex
updated addresses etc

\begin{document}
\title{Finding points on varieties with \emph{Macaulay2}}
\author{Sankhaneel Bisui}
\email{sbisui@tulane.edu}
\address{Department of Mathematics, Tulane University, New Orleans, LA 70118}
\author{Zhan Jiang}
\email{zoeng@umich.edu}
\address{Department of Mathematics, University of Michigan, Ann Arbor, MI 48109}
\author{Sarasij Maitra}
\email{sm3vg@virginia.edu}
\address{Department of Mathematics, University of Virginia, Charlottesville, VA 22904}
\author{Th\'ai Th\`anh Nguy$\tilde{\text{\^e}}$n}
\email{tnguyen11@tulane.edu}
\address{Department of Mathematics, Tulane University, New Orleans, LA 70118}
\author{Karl Schwede}
\email{schwede@math.utah.edu}
\address{Department of Mathematics, University of Utah, 155 S 1400 E Room 233, Salt Lake City, UT, 84112}
%\date{\today}

\thanks{Schwede was supported by NSF Grants \#1801849, FRG \#1952522 and a Fellowship from the Simons Foundation.}

>>>>

\begin{document}
\title{Finding points on varieties with \emph{Macaulay2}}
\author{Sankhaneel Bisui}
\email{Sankhaneel.Bisui@umanitoba.ca}
\address{Department of Mathematics, University of Manitoba, Winnipeg, MB R3T 2M8}
\author{Zhan Jiang}
\email{zoeng@umich.edu}
\address{Google, Mountain View, CA}
\author{Sarasij Maitra}
\email{maitra@math.utah.edu}
\address{Department of Mathematics, University of Utah, 155 S 1400 E Room 233, Salt Lake City, UT, 84112}
\author{Th\'ai Th\`anh Nguy$\tilde{\text{\^e}}$n}
\email{nguyt161@mcmaster.ca}
\address{Department of Mathematics, McMaster University, Hamilton, Ontario, L8S 4L8}
\author{Karl Schwede}
\email{schwede@math.utah.edu}
\address{Department of Mathematics, University of Utah, 155 S 1400 E Room 233, Salt Lake City, UT, 84112}
%\date{\today}

\thanks{Schwede was supported by NSF Grants \#1801849, \#2101800, FRG \#1952522 and a Fellowship from the Simons Foundation.}
